---
title: "Diffusion Curve Generator Output"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Introduction
These results are produced by diffusion curve generator hosted at [insert URL] and developed by The University of Sheffield.  The method underpinning the calculations is based on a paper by Sabine Grimm (see citation information at the end of this report)

The method takes probability distributions for three diffusion parameters to generate curves based on the Bass Model of Product Diffusion.  The parameters, $m$, $N1$ and $t'$, represent the maximum number of adoptions attained, the number of adoptions in the first year and the time at which the rate of diffusion reduces, respectively.

\pagebreak


# 2. Elicitation Input

Input distributions

```{r, echo=FALSE}
showInputData(dat)
```

Distributions of the input parameters (`r pars$Size` samples). `r ifelse(pars$Method=="mixture", "The parameters were sampled from mixture distributions.", "The parameters were linearly averaged")` 

```{r, echo=FALSE, fig.width=10, fig.height=3, fig.fullwidth=TRUE}
g <- visualise_inputs(pars)
```

Summary of sample input parameters
```{r, echo=FALSE}
summary(pars$Parameters[, c("M", "N1", "t")])
```

\pagebreak

# 3. Parameter fitting

Distributions of the fitted parameters (`r pars$Size` samples).
```{r, echo=FALSE, fig.width=10, fig.height=3, fig.fullwidth=TRUE}
g <- visualise_fitted(pars)
```

Summary of sample input parameters
```{r, echo=FALSE}
summary(pars$Parameters[, c("M", "p", "q")])
```

\pagebreak

# 4. Generated diffusion curves

Generated diffusion curves. `r if(input$curveType=="stats"){paste0("Statistics of ", input$avgType, " and ", input$centVal, "% quantiles showed.")}` 

- $N(t)$ Number of cumulated adoptions at $t$
- $dN(t)$ New adoptions at $t$

```{r, echo=FALSE, fig.width=10, fig.height=7, fig.fullwidth=TRUE}
visualise_curves(curves, dN=input$dnShow,  ci_range=input$centVal, statistics=input$curveType=="stats", average=input$avgType)
```

Average curves (`r input$avgType`)

```{r, echo=FALSE}
avg_curves
```

## Reference
Grimm SE, Stevens JW, Dixon S.  Estimating Future Health Technology Diffusion Using Expert Beliefs Calibrated to an Established Diffusion Model.  Value Health. 2018 Aug;21(8):944-950.